\section{Hardware}

\textbf{\acrfull{cpu} \index{CPU}} \\
\acrfull{cpu} is often referred to as the brain of the computer - with good reason. The CPU is meant to take care of a variety of tasks, very fast. 

\textbf{Motherboard \index{motherboard}} \\
The motherboard is the most important circuit board on a computer. Every major component is connected to the motherboard. This includes the CPU, GPU, sound card, RAM sticks. The motherboard also houses the BIOS tasked with starting up the computer. 

\textbf{GPU / Video card\index{GPU}\index{video card}} \\
While the CPU is meant to take care of a variety of tasks, the \acrfull{gpu} has one task - to render graphics by performing several mathematical operations alongside the CPU.  

\textbf{RAM \index{RAM}} \\
\acrfull{ram} contains the data required for the CPU to run a specific process (or several processed, depending on the size of the RAM). RAM is faster than your classical hard drive, but has less storage space. It is slower than the CPU's cache, but offers more space. 

\textbf{VRAM \index{VRAM}} \\
Video RAM is Video RAM. Just as the RAM feeds the CPU with data, the VRAM is tasked with feeding the GPU with data so images can be rendered to the screen. The data inside the VRAM is typically textures, frame buffers, shadow maps, bump maps and lightning. 

\textbf{Hard drive} \\

\textbf{SSD} \\

\textbf{Sound card}

\textbf{Router \index{router}} \\
A router is the traffic controller between your own home and the rest of the world. 

\textbf{Modem \index{modem}} \\
The data that get to your house through the cables are analog. A modem converts that signal to digital signals then passes it on to the router that figures out who the data was meant for and sends it their way. 

\textbf{Hotspot (WiFi)} \\




\newpage